Glyph-maps for visualizing climate data and models

### 2011-09-23 paper.tex
tweak

Other types of shifting and scaling can be useful. The mean and standard deviation might be used to standardize values, or the median and interquartile range, might be useful with some types of data. Shifting the values at each location to have mean zero, places more focus on the trend. This is particularly important for the star glyphs, where differences in the average value lead to unintuitive patterns in the resulting glyphs.  In this situation we would use $y_{st}-\bar{y}_s$ instead of $y_{st}$ in equations \ref{scale1}, \ref{scale2}, with minima and maxima calculated on the mean-shifted data.

>>>>

Other types of shifting and scaling can be useful. The mean and standard deviation might be used to standardize values, or the median and interquartile range, might be useful with some types of data. Shifting the values at each location to have mean zero, places more focus on the trend. This is particularly important for the star glyphs, where differences in the average value lead to unintuitive patterns in the resulting glyphs (eg Figure \ref{fig:cycle} star glyphs obscure the seasonal pattern).  In this situation we would use $y_{st}-\bar{y}_s$ instead of $y_{st}$ in equations \ref{scale1}, \ref{scale2}, with minima and maxima calculated on the mean-shifted data.
